To Do List

### 2019-04-20 Papers.Rmd

>>>>

- Jaroszewicz, Artur, and Jason Ernst. “An Integrative Approach for Fine-Mapping Chromatin Interactions.” Preprint. Bioinformatics, April 11, 2019. https://doi.org/10.1101/605576. - X-SCNN - prediction of significant Hi-C interactions at highly improved resolution using TFBSs, histone marks, DNAse data (WIG format). A Siamese Convolutional Neural Network (SCNN) - two subnetworks with shared parameters predicting true interactions. HiCCUPS calls as true interactions, the same number of no interactions (balanced dataset). Keras with TensorFlow backend.https://github.com/ernstlab/X-SCNN. Describe this paper and the references from introduction about the use of epigenomic data for prediction.
